Towards Performance-portable Parallel Programming in Computer Science Education

### 2020-01-21 src/2.Kokkos.tex
Updated images.
Small wording updates

A programming model is an abstract representation of a computer. It defines a paradigm and a programming language. The programming language is used by the programmer to write source code, a human readable, textual representation of instructions and data. Source code is a sequential listing of statements evaluated from the top to bottom, one line at a time. While such ordering seems natural to describe an algorithms as it corresponds to sequential processing (both, reading code and progressing the program counter follow a time line), it does not include the notion of concurrency.

@@

Semantic information provided by the programmer to the parallel programming model can be grouped into information to express intent and properties. They address the question of \emph{what}, \emph{where} and \emph{how}, which, in the context of parallel programming, corresponds to defining which code portion to parallelize, where to run and access and how to run that parallel code. Synchronization primitives may be considered as part of the what and information on the execution properties such as data placement or memory access type as the how. Semantics are expressed following a paradigm and a programming language.

@@

An instance of an \emph{execution space} is a specific instantiation of an execution space to which a programmer can target parallel work. For example, an execution space can be used to describe a multi-core processor. In this case, the execution space contains several homogeneous cores organized into arbitrary logical groups. In a parallel programming model that implements this machine model, an instance of such an execution space would be made available to the programmer to run kernels. Adding more logical groups or accelerators simply increases the number of available execution spaces to the programmer.

@@

%machine model

%\begin{figure}
%\centerline{\includegraphics[width=0.4\textwidth]{img/Stack.png}}
%\caption{Stack}
%\label{fig}
%\end{figure}

%\begin{figure}
%\centerline{\includegraphics[width=0.4\textwidth]{img/Abstractions.png}}
%\caption{Building workflow}
%\label{fig}
%\end{figure}

\begin{figure}
\centerline{\includegraphics[width=0.4\textwidth]{img/Stack.png}}
\caption{Landscaoe}
\label{fig:stack}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.4\textwidth]{img/Build.png}}
\caption{Building workflow}
\label{fig}
\end{figure}

>>>>

A programming model is an abstract representation of a computer. It defines a paradigm and a programming language. The programming language is used by the programmer to write source code, a human readable, textual representation of instructions and data. Source code is a sequential listing of statements evaluated from the top to bottom, one line at a time. While such ordering seems natural to describe an algorithm as it corresponds to sequential processing (both, reading code and progressing the program counter following a time line), it does not include the notion of concurrency.

@@

Semantic information provided by the programmer to the parallel programming model can be grouped into information to express intent and properties. They address the question of \emph{what}, \emph{where} and \emph{how}. In the context of parallel programming, these correspond to defining which code portion to parallelize, where to run and access and how to run that parallel code. Synchronization primitives may be considered as part of the what and information on the execution properties such as data placement or memory access type as the how. Semantics are expressed following a paradigm and a programming language.

@@

An instance of an \emph{execution space} is an abstraction over an execution resource to which a programmer can target parallel work. For example, an execution space can be used to describe a multi-core processor. In this case, the execution space contains several homogeneous cores organized into arbitrary logical groups. In a parallel programming model that implements this machine model, an instance of such an execution space would be made available to the programmer to run kernels. Adding more logical groups or accelerators simply increases the number of available execution spaces to the programmer.

@@

\begin{figure}
\centerline{\includegraphics[width=0.3\textwidth]{img/Stack.png}}
\caption{Landscape}
\label{fig:stack}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.3\textwidth]{img/Build.png}}
\caption{Building workflow}
\label{fig}
\end{figure}
